---
title: "Plotting network data"
output:
  html_document
---

I used Jesse Sadler's [amazingly comprehensive tutorial on plotting networks](https://www.jessesadler.com/post/network-analysis-with-r/) as a jumping board for all these plots.  

## Load packages

```{r message = FALSE}
library(dataone)
library(tidyverse)
library(network)
library(igraph)
library(tidygraph)
library(ggraph)
library(visNetwork)
library(networkD3)
library(data.tree)
```

## Get & organize data

I want to examine the nesting relationships of data packages on the [Arctic Data Center](https://arcticdata.io). In this case, I'm grabbing all packages with "Beard" as an author.

```{r}
cn <- dataone::CNode('PROD')
mn <- dataone::getMNode(cn,'urn:node:ARCTIC')

result <- dataone::query(mn, list(q = 'author:*Beard*',
                                  fl = '*',
                                  sort = 'dateUploaded+desc',
                                  rows='10000'),
                         as = "data.frame")
```

From the query results, I now extract the resource map information and transform the data to an "edge" structure. I want a `from` and a `to` column that describes the relationships between resource maps.

```{r}
get_query_edges <- function(result) {
  # resource maps (from) and their children (to)
  
  result %>% 
    as_tibble() %>% 
    filter(is.na(obsoletedBy)) %>% #remove any obsoleted resource maps from the mix
    select(resourceMap, documents) %>% 
    mutate(documents = str_split(documents, " ")) %>% #alternative to spread + gather
    unnest(documents) %>%
    filter(str_detect(documents, "resource")) %>% #grab only resource maps (ignores data and metadata objects)
    rename(from = resourceMap,
           to = documents) %>% 
    mutate_all(funs(str_replace(., "resource_map_", ""))) #remove "resource_map_" to reduce identifier lengths when plotting
}

edges <- get_query_edges(result)
```

## Plot data

```{r message = FALSE}
rm_network <- network::network(edges, matrix.type = "edgelist", ignore.eval = FALSE)
plot(rm_network, vertex.cex = 3)

rm_igraph <- igraph::graph_from_data_frame(d = edges, directed = TRUE)
plot(rm_igraph, edge.arrow.size = 0.2)
```

```{r}
rm_igraph_tidy <- tidygraph::as_tbl_graph(rm_igraph)
ggraph::ggraph(rm_igraph_tidy, layout = 'dendrogram', circular = TRUE) + 
  geom_edge_diagonal() + 
  geom_node_point() + 
  coord_fixed() +
  theme_graph()

ggraph::ggraph(rm_igraph_tidy, layout = "tree") +
  geom_edge_link() +
  geom_node_point() +
  # geom_node_text(aes(label = name), repel = TRUE) +
  theme_graph()
```

```{r}
#probably my favorite...
visNetwork::visIgraph(rm_igraph, 
          layout = "layout_as_tree",
          flip.y = FALSE)

networkD3::simpleNetwork(edges)

tree <- data.tree::FromDataFrameNetwork(as.data.frame(edges))
tree_list <- data.tree::ToListExplicit(tree, unname = TRUE)
networkD3::diagonalNetwork(tree_list)
```
