## Updating objects

You'll sometimes have to update data objects in a package, usually for one of two reasons:

1. The PI gives you a new version of the data file
2. You make changes to tidy up the data in accordance to [best practices](https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/0012-9623-90.2.205)

We want to archive data both in its raw form (straight from the PI) and in its improved form (edits by us), using provenance to link the two. 

Thus, in the case of (1), use `update_package_object` to update the data object with a new file, update the resource map, and update the EML (if it already has an associated data table/other entity). 

```{r eval = FALSE}
update_package_object(mnTest, 
                      data_pid = ORIGINAL_DATA_PID, 
                      new_data_path= NEW_DATA_PATH, 
                      resource_map_pid = RESOURCE_MAP_PID,
                      format_id = FORMAT_ID)
```

If YOU update a data object (to fix headers, etc.), then use `publish_object` followed by `publish_update` to keep the original and new data objects in the data package.

```{r eval = FALSE}
pkg <- get_package(mnTest, RESOURCE_MAP_PID)

new_pid <- publish_object(mnTest,
               path = NEW_DATA_PATH,
               format_id = FORMAT_ID,
               public = FALSE)

publish_update(mnTest,
               metadata_pid = pkg$metadata,
               resource_map_pid = pkg$resource_map,
               data_pids = c(pkg$data, new_pid), #add new pid
               child_pids = pkg$child,
               public = FALSE)
```

If you then need to make further updates to YOUR data object, then go ahead and use `update_package_object`:

```{r eval = FALSE}
update_package_object(mnTest, 
                      data_pid = YOUR_ORIGINAL_DATA_PID, 
                      new_data_path= NEW_DATA_PATH, 
                      resource_map_pid = RESOURCE_MAP_PID,
                      format_id = FORMAT_ID)
```

